---
title: "QAC305 Project"
author: "Ryan McGuffee, Xhonia Robinson, and Elliot Williams"
date: "5/9/2018"
output: html_document:
  toc: true
  toc_float: false
  code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Problem Statement
What is the problem you are trying to understand? Why is it important or useful to gain insight into
this problem?
  

## Data Description
Describe the dataset in detail. What is the source? How was it collected? What are the variables?
What are the characteristics of the variables?

```{r cars}
# this is just an example of an R code chunk. don't use this!
summary(cars)
```  
## Data Preprocessing

Describe any variable transformations, treatment of missing values, recoding and any other data
manipulations completed.

## Statistical Approaches

Describe your analytic techniques in detail. Assume that your audience is not familiar with the
techniques that you are using.

## Results

Describe the results in detail. What did you find. This the section for tables and graphs. You want
to communicate your results as clearly and compellingly as possible.

## Discussion

What did you find? What are the implications for policy? What suggestions do you have for other
researchers who want to take your work further?

## References

Standard reference section (similar to any term paper)